\documentclass{beamer}
\usetheme{Warsaw}
\usepackage{subfig}
\usepackage{listings}

\author{Cameron Gray}
\title{UG4 Project - IT Infrastructure Monitoring System}

\begin{document}
	\frame{\titlepage}
	\begin{frame}
		\frametitle{What is the project?}
		To build a complete, self contained system to monitor IT infrastructure in small and
		medium-sized enterprises.
		\pause
		\begin{itemize}
			\item Provide both time series monitoring and real time alerting
			\pause
			\item Can be managed entirely from a central interface
			\pause
			\item Support for plugins to monitor specialised hardware
		\end{itemize}
	\end{frame}
		
	\begin{frame}
		\frametitle{Components}
		System is split up into 3 components
		\begin{itemize}
			\item Agent
			\item Core
			\item Web
		\end{itemize}
	\end{frame}
		
	\begin{frame}[t]
		\frametitle{Agent}
		\begin{itemize}
			\item Runs on every machine being monitored.
			\item Provides a REST API over HTTPS to allow the core to connect to it and to
				retrieve data.
			\item Handles the installation and execution plugins				
		\end{itemize}	
		\pause
		\begin{definition}[Plugin]
			A plugin is a user provided package containing code to retrieve a custom metric
			from a machine.  For example you may have a plugin to check the CPU load average
			of a machine or to read the status of the arrays configured on a hardware RAID
			card.
		\end{definition}			
	\end{frame}
	
	\begin{frame}
		\frametitle{Core}
		The core handles most of the monitoring and data collection operations within Prophasis.
		It has 3 main roles:
		\begin{itemize}
			\item Scheduling
			\item Dispatching
			\item Alerting
		\end{itemize}
	\end{frame}
	
	\begin{frame}
		\frametitle{Web}
		\begin{itemize}
			\item Allows management of the system configuration	
			\item Provides an interface to view and analyse collected data
			\item Fully responsive design for use on mobile devices
		\end{itemize}
	\end{frame}
	
	\begin{frame}
		\frametitle{Demo!}
		
		\begin{center}
			\huge Live demo!
			
			\tiny Hopefully...
		\end{center}		
	\end{frame}
	
	\begin{frame}
		Questions?
	\end{frame}
\end{document}